Analysis of epistatic inflation under large single additive effects, with a focus on the replication rate

### 2019-09-30 null_replication/docs/analyse_results.rmd
reorganised

- that discovering associations at experiment wide thresholds (e.g. 1e-16) is unlikely even when the lambda is very high
- the replication rate could be quite high using FDR
- the replication rate is very low at experiment wide thresholds
- we might get higher experiment wide replication rates if we found a way that the discovery effects surpassed the experiment wide threshold

>>>>

- that discovering associations at experiment wide thresholds (e.g. 1e-16) is unlikely even when the lambda is very high
- the replication rate could be quite high using FDR, even if the lambda is very low
- the replication rate is very low at experiment wide thresholds
- we might get higher experiment wide replication rates if we found a way that the discovery effects surpassed the experiment wide threshold
